Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-03 doc/prelim/presentation/prelim_presentation.tex
removing experimental framework slide
cleaning up gmres slide
removing mcsa derivation slides

  \begin{itemize}
  \item Yields the normal system $\ve{A}^T\ve{A}\ve{x} =
    \ve{A}^T\ve{b}$
  \item Must generate an orthonormal basis $\ve{V}_m \in \mathbb{R}^{N
    \times m}$ for $\mathcal{K}_m(\ve{A},\ve{r}_0)$
  \item Typically choose a Gram-Schmidt-like procedure such as Arnoldi
    or Lanzcos
  \item Short and long recurrence relations available for
    orthogonalization
  \end{itemize}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Monte Carlo Synthetic-Acceleration}
  \begin{itemize}
  \item Evans and Mosher 2009 work
  \item Split the operator to yield Richardson's iteration
  \end{itemize}

  \[
  \ve{x} = (\ve{I} - \ve{A})\ve{x} + \ve{b}
  \]
  \[
  \ve{x}^{k+1} = (\ve{I} - \ve{A})\ve{x}^k + \ve{b}
  \]

  \begin{itemize}
  \item Define the iteration error
  \end{itemize}

  \[
  \delta \ve{x}^k = \ve{x} - \ve{x}^k
  \]
  \[
  \delta \ve{x}^{k+1} = (\ve{I} - \ve{A})\delta \ve{x}^k
  \]

@@

  \begin{itemize}
  \item Subtract $(\ve{I} - \ve{A})\delta \ve{x}^{k+1}$
  \end{itemize}

  \[
  \begin{split}
    \ve{A}\delta \ve{x}^{k+1} &= (\ve{I} -
    \ve{A})(\ve{x}^{k+1}-\ve{x}^{k}) \\ &= \ve{r}^{k+1}
  \end{split}
  \]

  \begin{itemize}
  \item The following converges in one iteration with exact inversion
    of $\ve{A}$:
  \end{itemize}

  \[
  \ve{x}^{k+1} = (\ve{I} - \ve{A})\ve{x}^k + \ve{b}
  \]
  \[
  \ve{A} \delta \ve{x}^{k+1} = \ve{r}^{k+1}
  \]
  \[
  \ve{x} = \ve{x}^{k+1} + \delta \ve{x}^{k+1}
  \]

@@

  \begin{itemize}
  \item Experimental framework
  \item Methods verification
  \item Numerical experiments
  \item Challenge problem
  \end{itemize}

%%---------------------------------------------------------------------------%%
\begin{frame}{Experimental Framework}

  \begin{itemize}
  \item Need a framework to generate linear and nonlinear systems in
    parallel
    \begin{itemize}
    \item Linear algebra data structures
    \item Parallel communication framework
    \item Mesh generation and partitioning
    \item Automatic differentiation and more...
    \end{itemize}
  \item Choose the finite element method to leverage a finite element
    assembly engine
  \end{itemize}

  \[
  \ve{A}(\ve{u}) = \ve{0},\ \forall \ve{u} \in \Omega
  \]
  \[
  \ve{B}(\ve{u}) = \ve{0},\ \forall \ve{u} \in \Gamma
  \]
  \[
  \int_{\Omega} \ve{v}^T \ve{A}(\ve{u}) d\Omega + \int_{\Gamma}
  \bar{\ve{v}}^T \ve{B}(\ve{u}) d\Gamma = \ve{0}
  \]
  \[
  \int_{\Omega} \ve{C}(\ve{v}^T) \ve{D}(\ve{u}) d\Omega +
  \int_{\Gamma} \ve{E}(\bar{\ve{v}}^T) \ve{F}(\ve{u}) d\Gamma = \ve{0}
  \]

>>>>

  \begin{itemize}
  \item Yields the normal system $\ve{A}^T\ve{A}\ve{x} =
    \ve{A}^T\ve{b}$
  \item Must generate an orthonormal basis for
    $\mathcal{K}_m(\ve{A},\ve{r}_0)$
  \item Typically choose a Gram-Schmidt-like procedure such as Arnoldi
    or Lanzcos
  \item Short and long recurrence relations available for
    orthogonalization
  \end{itemize}

@@

@@

  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {MCSA Iteration (Evans,2009)}

@@

  \begin{itemize}
  \item Methods verification
  \item Numerical experiments
  \item Challenge problem
  \end{itemize}
